---
title: "demo_R"
author: "Antonio Ruiz"
date: "June 11, 2019"
output: rmarkdown::github_document
---


```{r}

print('hello world')

```





## Vectors
```{r}

A_vector <- c(1, 2, 3)
B_vector <- c(4, 5, 6)

# Take the sum of A_vector and B_vector
total_vector <- A_vector %*% B_vector
  
# Print out total_vector
total_vector


```

## some basic plotting and filters
```{r}
library(tidyverse)

ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy))

filter(mpg, cyl == 8)

filter(diamonds, carat > 3)
```

## Loading DatasauRus


```{r}
library(datasauRus)

datasaurus_dozen %>% count(dataset) %>% print(13)

#?datasaurus_dozen


```


```{r}

datasaurus_dozen
```
## Exercise 1 Response:
* Description: A dataset demonstrating the utility of visualization. These 12 datasets are equal in standard measures: mean, standard deviation, and Pearson's correlation. 
* Columns: 3
* Rows: 1846
* Each row is a set of coordinates with a respective data.

## Dino Data Frame
```{r}

dino_data <- datasaurus_dozen %>% filter(dataset =="dino")
```

## Some GGPlot
  * Answer to question:


## Exercise 2
* Plotting x vs y,
* Correlation: -0.06447185
```{r}
ggplot(data=dino_data, mapping=aes(x=x,y=y)) + geom_point()

cor(dino_data$x, dino_data$y)
```


```{r}
dino_data %>% summarize(r = cor(x,y))
```


