---
title: "demo_R"
author: "Antonio Ruiz"
date: "June 11, 2019"
output: rmarkdown::github_document
---


## some basic plotting and filters
```{r}
library(tidyverse)

ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy))

filter(mpg, cyl == 8)

filter(diamonds, carat > 3)
```

## Loading DatasauRus


```{r}
library(datasauRus)

datasaurus_dozen %>% count(dataset) %>% print(13)

#?datasaurus_dozen


```

## Exploring the dataset
```{r}

datasaurus_dozen

table(datasaurus_dozen$dataset)
```
## Exercise 1 Response:
* Description: A dataset demonstrating the utility of visualization. These 12 datasets are equal in standard measures: mean, standard deviation, and Pearson's correlation. 
* Columns: 3
* Rows: 1846
* Each row is a set of coordinates with a respective data.


## Exercise 2
* Plotting x vs y,
* Correlation: -0.06447185
```{r}

dino_data <- datasaurus_dozen %>% filter(dataset =="dino")

ggplot(data=dino_data, mapping=aes(x=x,y=y)) + geom_point()

cor(dino_data$x, dino_data$y)
```


```{r}
dino_data %>% summarize(r = cor(x,y))
```





## Exercise 3
* Plotting x vs y,
* Correlation:  -0.0629611
* Response: Very similar 'weak' correlation to the dino data set
```{r}
star_data <- datasaurus_dozen %>% filter(dataset =="star")

ggplot(data=star_data, mapping=aes(x=x,y=y)) + geom_point()

cor(star_data$x, star_data$y)
```




## Exercise 4
* Plotting x vs y for Circle Dataset
* Correlation: -0.06834336
* Response: Very similar 'weak' correlation to the dino data set, slightly higher negative correlation
```{r}
star_data <- datasaurus_dozen %>% filter(dataset =="circle")

ggplot(data=star_data, mapping=aes(x=x,y=y)) + geom_point()

cor(star_data$x, star_data$y)
```



